%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Manav S. Mehta} \\ \vspace{1pt}
    Mumbai, Maharashtra, India \\ \vspace{1pt}
%
    %    \small \raisebox{-0.1\height}
%    \faPhone\ 123-456-7890 ~ 
    \href{https://google.com/}{\raisebox{-0.2\height}\faCompass\ \underline{google.com}} ~
    \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{email@gmail.com}} ~ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/username}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/username}}
    \vspace{-8pt}
\end{center}

%
%-----------EDUCATION-----------
%\section{Education}
 % \resumeSubHeadingListStart
  %  \resumeSubheading
   %   {Mumbai University}{May 2019}
    %  {Bachelor of Engineering in Information Technology}{Mumbai, Maharashtra}
  %\resumeSubHeadingListEnd
%\vspace{0.5pt}

%
%------RELEVANT COURSEWORK-------
%\section{Relevant Coursework}
    %\resumeSubHeadingListStart
 %       \begin{multicols}{4}
  %          \begin{itemize}[itemsep=-5pt, parsep=3pt]
   %             \item\small Data Structures
    %            \item Software Methodology
     %           \item Algorithms Analysis
      %          \item Database Management
       %         \item Artificial Intelligence
        %        \item Internet Technology
         %       \item Systems Programming
          %      \item Computer Architecture
           % \end{itemize}
        %\end{multicols}
        %\vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd
%

%-----------Summary-----------
\section{Summary}
Skilled software engineer with hands-on experience in .NET framework, SQL, and Open Source IoT. 
Strong team player with excellent communication and leadership skills. 
Proven ability to guide and mentor team members and eager to continue learning and growing with an organization.
\vspace{0.5pt}
%

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    %\resumeSubheading
     % {Electronics Company}{City, State}
      %{Software Engineer}{May 2020 -- August 2020}
      %\resumeItemListStart
       % \resumeItem{Developed a service to automatically perform a set of 
        %unit tests daily on a product in development in order to decrease 
        %time needed for team members to identify and fix bugs/issues.}
       % \resumeItem{Incorporated scripts using Python and PowerShell to 
        %aggregate XML test results into an organized format and to load 
        %the latest build code onto the hardware, so that daily testing can be performed.}
       % \resumeItem{Utilized Jenkins to provide a continuous integration 
        %service in order to automate the entire process of loading the 
        %latest build code and test files, running the tests, and generating a 
        %report of the results once per day.}
       % \resumeItem{Explored ways to visualize and send a daily report of 
        %test results to team members  using HTML, Javascript, and CSS.}
       % \resumeItem{Developed a service to automatically perform a set of 
        %unit tests daily on a product in development in order to decrease 
        %time needed for team members to identify and fix bugs/issues.}
       % \resumeItem{Incorporated scripts using Python and PowerShell to 
        %aggregate XML test results into an organized format and to load 
        %the latest build code onto the hardware, so that daily testing can be performed.}
       % \resumeItem{Utilized Jenkins to provide a continuous integration 
        %service in order to automate the entire process of loading the 
        %latest build code and test files, running the tests, and generating a 
        %report of the results once per day.}
       % \resumeItem{Explored ways to visualize and send a daily report of 
        %test results to team members  using HTML, Javascript, and CSS.}
      %\resumeItemListEnd

      \resumeSubheading
      {ANV Infotech Pvt. Ltd.}{Nagpur, Maharashtra}
      {Software Engineer}{February 2020 -- February 2022}
      \resumeItemListStart
        \resumeItem{Led the design and development of a custom IoT system using Arduino, assisted in the patent application process and early marketing strategy.}
        \resumeItem{Managed and developed the codebase for new IoT projects and worked in an agile team to prioritize and develop features for a custom IoT board based on Arduino, and scope requests to prioritize work on modules with the biggest impact.}
        \resumeItem{Created and maintained technical documents, provided training to clients and internal stakeholders on company products and services, and assisted with troubleshooting and provided technical support.}
        \resumeItem{Conducted on-site demonstrations, trainings, and presentations, and responded to and resolved customer issues and reported to senior support and development team.}
        \resumeItem{Trained new team members and mentored them, participated in support work as needed.}
        \resumeItem{Implemented cost-saving measures by shifting from Microsoft Visio to Draw.io and training the staff, resulting in an annual savings of 50,000 INR.}
      \resumeItemListEnd

    \resumeSubheading
      {ANV Infotech Pvt. Ltd.}{Nagpur, Maharashtra}
      {Graduate Engineering Trainee}{November 2019 -- January 2022}
      \resumeItemListStart
        \resumeItem{Assisted in development of IoT projects comprising of Arduino and tested the proper running of the code.}
        \resumeItem{Created technical documentation, including design diagrams, for the company's custom systems and assisted with troubleshooting and provided technical support for company products.}
        \resumeItem{Helped in preparing for presentations, and product outreach and assisted in product demonstrations, training and support to clients.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{0.5pt}
%

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress} \\
    }}
 \end{itemize}
\vspace{0.5pt}
%

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Mumbai University}{May 2019}
      {Bachelor of Engineering in Information Technology}{Mumbai, Maharashtra}
  \resumeSubHeadingListEnd
\vspace{0.5pt}
%

%-----------OTHER EXPERIENCE-----------
\section{Other Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Santactuz Tank Lane School}{Mumbai, Maharashtra}
      {IT Consultant}{May 2020 -- May 2021}
      \resumeItemListStart
        \resumeItem{Delivered training on the use of Microsoft Office, video conferencing platforms, Windows OS and basic to advanced computer usage resulting in a 90\% reduction in task completion time and an 80\% reduction in extending deadlines.}
        \resumeItem{Assisted in the setup of Zoom, Google Classrooms and Google Meet for students and teachers on a regular basis, and provided instruction for over 50 students on effective online learning methods.}
        \resumeItem{Managed all school online responsibilities and facilitated a seamless transition from in-person to online instruction, and digitized all documents from the previous academic year and converted offline paperwork to digital format.}
        \resumeItem{Provided technical support for hardware and software related issues, documented all school events and activities for the academic year 2020-2021, and created presentations and documents for online events.}
        \resumeItemListEnd

    \resumeSubheading
      {SAKEC Speaker's Club}{Mumbai, Maharashtra}
      {Technical Head}{September 2018 -- May 2019}
      \resumeItemListStart
        \resumeItem{Successfully organized and managed all technical aspects for over 10 college events as the technical head, coordinating with other event committee heads and leading a team of 5 members to ensure smooth event operation.}
        \resumeItem{Recruited, trained and provided leadership to new students and technical team members to execute events and ensure proper progress.}
    \resumeItemListEnd

    \resumeSubheading
    {SAKEC Speaker's Club Inter-College Quiz}{Mumbai, Maharashtra}
    {Technical Head}{October 2018}
      \resumeItemListStart
        \resumeItem{Successfully organized and managed all technical aspects for an intercollege quiz with over 200 participants, delegating responsibilities and ensuring smooth execution.}
        \resumeItem{Designed and implemented a custom buzzer system using Arduino programming to facilitate the quiz portion of the event.}
        \resumeItem{Coordinated and managed vendor communication for refreshments and meals during the event.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{0.5pt}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gym Reservation Bot} $|$ \emph{Python, Selenium, Google Cloud Console}}{January 2021}
          \resumeItemListStart
            \resumeItem{Developed an automatic bot using Python and Google Cloud Console to register myself for a timeslot at my school gym.}
            \resumeItem{Implemented Selenium to create an instance of Chrome in order to interact with the correct elements of the web page.}
            \resumeItem{Created a Linux virtual machine to run on Google Cloud so that the program is able to run everyday from the cloud.}
            \resumeItem{Used Cron to schedule the program to execute automatically at 11 AM every morning so a reservation is made for me.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Ticket Price Calculator App} $|$ \emph{Java, Android Studio}}{November 2020}
          \resumeItemListStart
            \resumeItem{Created an Android application using Java and Android Studio to calculate ticket prices for trips to museums in NYC.}
            \resumeItem{Processed user inputted information in the back-end of the app to return a subtotal price based on the tickets selected.}
            \resumeItem{Utilized the layout editor to create a UI for the application in order to allow different scenes to interact with each other.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Transaction Management GUI} $|$ \emph{Java, Eclipse, JavaFX}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed a sample banking transaction system using Java to simulate the common functions of using a bank account.}
            \resumeItem{Used JavaFX to create a GUI that supports actions such as creating an account, deposit, withdraw, list all acounts, etc.}
            \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{0.5pt}
%
%-----------PROGRAMMING SKILLS-----------
%\section{Technical Skills}
 %\begin{itemize}[leftmargin=0.15in, label={}]
  %  \small{\item{
   %  \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL} \\
    % \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio} \\
     %\textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress} \\
    %}}
 %\end{itemize}
 %\vspace{-16pt}


%-----------INVOLVEMENT---------------
%\section{Leadership / Extracurricular}
 %   \resumeSubHeadingListStart
  %      \resumeSubheading{Fraternity}{Spring 2020 -- Present}{President}{University Name}
   %         \resumeItemListStart
    %            \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
     %           \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
      %          \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
       %     \resumeItemListEnd
        
    %\resumeSubHeadingListEnd


\end{document}
